\documentclass[9pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontspec}
\setmainfont{DejaVu Sans}
\setlist{nosep,leftmargin=*}
\titlespacing*{\section}{0pt}{8pt}{4pt}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}
\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE \textbf{Partner with Pearl Memorial}}\\[3pt]
{\large Building Community Resilience Together}
\end{center}

\vspace{8pt}

\begin{multicols}{2}

\subsection*{Why This Matters to Your Business}
The 2023 Lahaina fires showed us: \textbf{when communities suffer, everyone suffers.} Hotels lose staff. Restaurants lose customers. Gas stations lose power. Churches lose congregations.

Pearl Memorial works directly with Maui communities to build \textbf{off-grid resilience systems} — power, communication, and emergency preparedness that keeps families and businesses running when disaster strikes.

\subsection*{What We Do}
\begin{itemize}
\item \textbf{Off-Grid Power} — Solar, generators, battery storage
\item \textbf{Emergency Communication} — Satellite phones when grids fail
\item \textbf{Community Workshops} — Gift economy events, skill building
\item \textbf{Knowledge Transfer} — Training to maintain and share resources
\end{itemize}

\subsection*{Who We Work With}
\begin{itemize}
\item \textbf{Hotels \& Resorts} — Employee housing resilience, CSR programs
\item \textbf{Restaurants \& Food Trucks} — Backup power for refrigeration
\item \textbf{Gas Stations \& General Stores} — Emergency supply hubs
\item \textbf{Ranches \& Farms} — Off-grid water pumping, livestock care
\item \textbf{Churches \& Community Orgs} — Gathering space resilience
\end{itemize}

\subsection*{About Us}
A Japanese family bridging Japan and Hawaii — 150 years of shared history. 3 years of R\&D, now hands-on in Maui since 2025.

\textbf{2025 Track Record:}
\begin{itemize}
\item 3+ households with off-grid systems
\item 5 community workshops conducted
\item Church \& farm partnerships established
\end{itemize}

\columnbreak

\subsection*{Partnership Levels}
\begin{itemize}
\item \textbf{Starter} (\$500–4,000) — Workshop supplies, transportation
\item \textbf{Builder} (\$4,000–6,000) — Full household backup system
\item \textbf{Operate} (\$6,000+) — Builder kit + ongoing fuel \& connectivity
\item \textbf{Visionary} (\$100,000+) — Community-scale infrastructure
\end{itemize}

\subsection*{What You Receive}
\begin{itemize}
\item \textbf{All Partners:} Annual Gratitude Report listing
\item \textbf{All Partners:} Quartz glass engraving (10,000+ year archive)
\item \textbf{Builder+:} Featured in storytelling content
\item \textbf{Visionary:} Permanent website recognition
\item \textbf{Visionary:} Project naming rights (e.g., "[Your Brand] Community Resilience Hub")
\end{itemize}

\subsection*{Why Partner With Us?}
\begin{itemize}
\item \textbf{Direct Impact} — 100\% goes to equipment and operations
\item \textbf{Full Transparency} — Detailed reporting on fund usage
\item \textbf{Local Presence} — We live and work in Maui, hands-on
\item \textbf{Employee Benefit} — Prioritize support for your staff's families
\item \textbf{CSR Storytelling} — Content for your sustainability reports
\end{itemize}

\subsection*{Let's Talk}
\textbf{Book a conversation:}\\
calendly.com/pearlmemorial/pearlmemorialsession

\textbf{Email:} business@satotakuya.jp

\textbf{Instagram:} @pearl.memorial

\vspace{6pt}
\textit{We accept bank transfers (US \& Japan), crypto, and alternative arrangements.}

\end{multicols}

\vspace{8pt}
\begin{center}
\rule{0.8\textwidth}{0.4pt}\\[6pt]
{\large \textbf{Pearl Memorial}}\\
\textit{Resilience through connection. Recovery through action.}
\end{center}

\end{document}
